Lawrence Bull, PhD

### 2024-08-28 index.qmd
UoG, LI and X links

Researcher in statistical methods for Data-Centric Engineering, specialising in monitoring techniques for telemetry data from systems and infrastructure.

@@

@@

[twitter](https://twitter.com/lwrncebull?lang=ar)

>>>>

Researcher Fellow at [Glasgow University](https://www.gla.ac.uk/schools/mathematicsstatistics/staff/lawrencebull/#biography) in statistical methods for Data-Centric Engineering, specialising in monitoring techniques for telemetry data from systems and infrastructure.

@@

[LinkedIn](https://www.linkedin.com/in/lawrence-bull-793178109/)

@@

[X](https://x.com/lwrncebull)
